### 2018-05-06 papers/synth/model.tex
appendix fix

We have extended the model by considering each complex molecule as distinct. In the previous paper, we have considered three Q SNARES as a single molecule. We also do not assume that SNARE type distribution is even in the whole system. The fusion is now driven by the active presence of three Q SNARE and one R SNARE molecule, present in any combination on edge and on the target compartment. We have relaxed the pairing matrix constraint to comply with this fact. In order for the biological efficiency and optimality reasons we still do not allow self-edges to be present in the VTS. 
%\begin{enumerate} 
%\item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
%\item In the graph shown the R-SNAREs are always in active. Every combination is formed by three active Q-SNAREs and one active R-SNARE.
%\item  Qai, Qbi, Qci and Ri are just dummy names, real biological names can be found in the below table. 
%\item In the diagram white circle molecules are always active. Other edge labels are inactive molecules.
%\item Pairing matrix restriction: ith R-SNARE can fuse with only the corresponding ith Q-SNARES and vice-versa. No other combination is allowed.
%\end{enumerate}

>>>>

In the previous paper, we have considered three Q SNARES as a single molecule. We have extended this model by considering each complex molecule as distinct. In contrast to the previous model we allow SNARE type distribution across the whole system to be uneven. The fusion is now driven by the active combination of three Q SNARE and one R SNARE molecule. We have relaxed the pairing matrix constraint to comply with this fact. For biological efficiency and optimality reasons we do not allow self-edges to be present in the VTS. 
%\begin{enumerate} 
%\item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
%\item In the graph shown the R-SNAREs are always in active. Every combination is formed by three active Q-SNAREs and one active R-SNARE.
%\item  Qai, Qbi, Qci and Ri are just dummy names, real biological names can be found in the below table. 
%\item In the diagram white circle molecules are always active. Other edge labels are inactive molecules.
%\item Pairing matrix restriction: ith R-SNARE can fuse with only the corresponding ith Q-SNARES and vice-versa. No other combination is allowed.
%\end{enumerate}
